---
output: rmarkdown::github_document
---

# mactheknife

Read 'macOS' .DS_Store' Files 

## Description

A thin wrapper around the 'Python' 'dsstore' module <https://github.com/gehaxelt/Python-dsstore> by 'Sebastian Neef'.

## NOTE

- This may turn into a broader "macOS hacking" package
- Uses `reticulate` so a working Python implementation is needed

## What's Inside The Tin

- `read_dsstore`:	Read a '.DS_Store' file

The following functions are implemented:

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/mactheknife")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(mactheknife)

# current verison
packageVersion("mactheknife")

```

## Built-in data

```{r}
read_dsstore(
  path = system.file("extdat", "DS_Store.ctf", package = "mactheknife")
)
```

## My "~/projects" folder (use your own dir as an example)

```{r}
library(magrittr)

list.files(
  path = "~/projects", pattern = "\\.DS_Store", 
  all.files=TRUE, recursive = TRUE, full.names = TRUE
) %>% 
  lapply(read_dsstore) -> x

str(x)
```
